


%\subsection{Buffer Insertion}
%%For buffer insertion problem, van Ginneken's algorithm~\cite{Lukas:Buffer} is considered to be a classic in the field. Given a fixed buffer tree and candidate buffer locations, it finds the optimal buffer solutions under Elmore delay models. Several papers extend the algorithm to handle library with multiple buffers, various kinds of constraints and delay models and wire sizing integration~\cite{Lillis:Optimal,Alpert:Wire,Alpert:Buffer,Lillis:Simultaneous,Cong:Buffer,Wong:A}. A significant limitation of van Ginneken's algorithm is that a fixed Steiner topology must be provided in advance. Several papers address the tree construction problems, including C-Tree Algorithm~\cite{Alpert:Buffered}, P-Tree Algorithm~\cite{Lillis:New} and S-Tree Algorithm~\cite{Hrkic:S}.
%
%In this contest, to minimize the area when inserting buffers, we only choose the smallest buffer available in the cell library. Also since we are considering the problem under multiple corners, we will choose the $\star$ worst corner to perform buffer insertion. Notice that this step is not aim to fix all the timing violations, but to just reduce the capacitance load of those high fan-out nets, and any remaining violations and optimization problems will be left to gate sizing section.
%
%We adopt the ideas presented in C-Tree Algorithm~\cite{Alpert:Buffered}, followed by van Ginneken's algorithm~\cite{Lukas:Buffer}. Since we are only going to insert buffers for high-fan-out nets without an RC-tree (which means ideal wires), we might want to modify the existing algorithm a little bit and we will not construct the specific steiner tree construction as described in~\cite{Alpert:Buffered}. We will start by performing 2-clustering, which separate the sinks with similar characteristics (criticality and capacitance) into two clusters recursively, from top to the bottom, until each cluster has no more than 2 sinks. This step essentially create a binary tree where each branching point is a potential position for a buffer. Then, the van Ginneken's algorithm~\cite{Lukas:Buffer} can be applied to determine the optimal buffer insertion solution for the given topology.
%
%Since the solution quality heavily depends on the initial topology we construct, we need to give a good clustering metric between pairs of points (sinks). Due to the ideal wire-model assumption of these nets for buffer insertion in this contest, our clustering metric is slightly different from that presented in~\cite{Lukas:Buffer}. In our implementation, sinks nodes are clustered based on the slack and the capacitance value. We adopt similar idea presented in the paper and the criticality distance between two sink nodes $s_i$ and $s_j$, $tDist(s_i, s_j) = |crit(s_i) - crit(s_j)|$ and
%\begin{equation}
%crit(s_i) = e^{\alpha(mAS - AS(s_i))/(aAS - mAS)}
%\end{equation}
%where $AS(s_i)$ is the slack of the sink node $s_i$, $mAS$ and $aAS$ are the minimum and the average slack for all the sinks, and $\alpha > 0$ is a user parameter. Since the buffers are inserted in an ideal wire in our problem, we also have $AS(s_i) = RAT(s_i)$, so are $mAS$ and $aAS$. Furthermore, our problem consider multiple corners, and we will just choose the corner which gives the worst slack for each sink so that the algorithm gives the buffer insertion solution under the worst case.
%
%The capacitance distance definition is different. Since we want to separate the two sinks whenever they lead to large total capacitance, a reasonable normalized capacitance distance definition between two sink nodes $s_i$ and $s_j$, $cDist(s_i, s_j)$ will be $|ncap(s_i) + ncap(s_j)|$, where
%\begin{equation}
%ncap(s_i) = \frac{cap(s_i)}{\Sigma_i cap(s_i)},
%\end{equation}
%The final distance $D(s_i, s_j)$ is simply defined as the summation of the two distances:
%\begin{equation}
%D(s_i, s_j) = tDist(s_i, s_j) + cDist(s_i, s_j).
%\end{equation}
%%we are going to use in clustering will be the Euclidean distance defined as:
%%\begin{equation}
%%D(s_i, s_j) = \sqrt{tDist(s_i, s_j)^2 + cDist(s_i, s_j)^2}.
%%\end{equation}

\section{Gate Sizing}
\label{sec:gate_sizing}

We use gate sizing to optimize for setup time, area and leakage power, while not introducing hold time violations and satisfying maximum slew requirement.
%Gate sizing problems are also well studied in the literature. TILOS~\cite{Fishburn:TILOS} applied Greedy method to gate sizing and modeled delay and slew functions as posynomials. The paper~\cite{Sapatnekar:An} provided a geometric programming approach, which is guaranteed to find the global optimal solution, to solve the transistor sizing problem. Lagrangian Relaxation is also widely used in both continuous gate sizing~\cite{Chen:Fast} and discrete gate sizing~\cite{Liu:A}, and it provides scalable methods to large instances. Faster approaches for gate sizing in practice given predefined discrete cell libraries are delay budget approaches~\cite{Chen:iCOACH,Dai:MOSIZ}, which repeatedly distribute delay budgets to cells and can manage interactions between gates~\cite{Held:Gate}. Slew target can also be distributed instead of delay budgets as an alternative, based on the assumption that the delay is a monotonic function of the slew. Most of other discrete gate sizing methods ignore the slew, and compared to these work, the slew targeting method enables a more accurate gate sizing~\cite{Held:Gate}.

In this contest, we implement the slew targeting method introduced by Held in~\cite{Held:Gate}, because (1) it directly addresses slew violations, (2) it avoids a large number of incremental timing updates, and (3) it is highly parallelizable. Since the paper focuses on fixing setup time violations, we generalize the method a little bit to handle hold time violations.

%Slew target approach~\cite{Held:Gate} also turns out to give more accurate gate sizing solutions than delay budget approach~\cite{Chen:iCOACH,Dai:MOSIZ}. Furthermore, it is a graph-based algorithm, which well adapts to our Galois system. Since the paper focuses on fixing setup time violations, we generalize the method a little bit such that it also addresses hold time violations.

\subsection{Rationale behind Slew Targeting}

Slew targeting works by associating each gate output pin with a slew target to guide the gate sizing process~\cite{Held:Gate}. To upsize/downsize a gate, just decrease/increase the slew target of its output pins. To facilitate MCMM optimization, each pin should have slew targets for all combinations of corners and delay modes.

The original slew targeting method assumes that delay and output slew are monotonic with respect to input slew. However, this assumption does not hold in general. For example, in the cell libraries given by the contest committee, this monotonicity does not hold when input slew is large and the output load is small for several cells. We think slew targeting still works in this case for two reasons: (1) The case when monotonicity does not hold is the situation we want to optimize away for the design; and (2) empirically, output slew and delay are weak functions of input slew, and the small fluctuations will not affect the accuracy of the final solution of our implementation by much.

In order for slew targeting to work, the following questions need to be addressed:
\begin{enumerate}
\item How to set the initial slew target for each gate output?
\item How to update the slew targets?
\item How to assign cells to gates?
\item When does the gate sizing converge?
\end{enumerate}

%Discrete gate sizing problem in the paper is stated as following: Given a circuit, we will assign each individual cell in the circuit a library cell from a discrete cell library, and the assignment should be chosen such that all the timing constraints are met (all the slack are non-negative) and the slew value at each pin is no larger than the slew limit value. Slew target method is based on the assumption that the delay is a monotonic function of the input slew. This assumption generally holds in practical design as can be seen in the cell library file, but there might be small fluctuations on delay/output slew vs input slew where the monotone property fail. Empirically, we do not have to worry about this because output slew and delay are weak functions of input slew, and the small fluctuations will not affect the accuracy of the final solution of our implementation by much.

%It turns out that slew target method gives more efficient and accurate gate sizing solutions. The assumption that the delay is a monotonic function of the slew generally holds, although some small fluctuations might exist, which should not affect the final solution by much. Furthermore, our Galois system provides better support for graph-based algorithms. Thus, in this contest, we are going to adopt the slew target method presented in~\cite{Held:Gate} for gate sizing.

\subsection{Slew Target Initialization}
We perform STA after buffer insertion and use the slew values as the initial slew targets.

\subsection{Slew Target Update}

Let $slewt(p)$ be the slew target of an output pin $p$ of gate $g$. In setup time analysis, if $p$ has a negative slack and it is on a critical path, we upsize $g$ by decreasing $slewt(p)$; otherwise, we downsize $g$ by increasing $slewt(p)$. In hold time analysis, the operation is opposite: downsize the gate when one of its output pins has negative slack and the pin is on a critical path, and upsize otherwise.

To know whether $p$ is on a critical path, we compute the local criticality of $p$, $lc(p)$, as follows. Let $slack^{-}(g) = \min\{slack(i) | (i, j) \in W \land j \in input(g)\}$, where $W$ is the set of wires and $input(g)$ is the set of input pins for gate $g$. Then $lc(p) = \max\{slack(p) - slack^{-}(g), 0\}$. Note that if $p$ belongs to a combinational gate $g$, then $lc(p) \geq 0$, and $p$ is on a critical path if and only if $lc(p) = 0$. Since we only optimize for datapaths in between registers, this definition of $lc(p)$ suffices to guide the update of slew targets.

Now we elaborate how to update the value for slew target of $p$. Instead of computing the change in slew target based on slacks as in~\cite{Held:Gate}, we leverage the information in the given cell libraries to directly come up with new slew targets.

Tables~\ref{table:lib1} and~\ref{table:lib2} show the rising slews for pin Z of cell BUF\_X1 and that of BUF\_X2, respectively. Note that (1) both tables contain similar values, and (2) for a given input slew and output capacitance, the corresponding entry in Table~\ref{table:lib2} is left to the one in Table~\ref{table:lib1}, and the two entries are always on the same row. For example, for input slew value of 15.6743 and output capacitance value of 30.3269, the output slew is given by the entry at row 3 and column 6 in Table~\ref{table:lib1}, and by the entry at row 3 and column 5 in Table~\ref{table:lib2}. This relation also holds for other types of functionally equivalent cells with different sizes across all corners. Therefore, the slew target of $p$ can be updated according to a sequence of numbers derived through table look-up into output slew tables using current input slew and different output capacitance. We call this sequence the slew possibilities of $p$.

To upsize/downsize a gate $g$ to which pin $p$ belongs, we take smaller/larger terms in $p$'s slew possibilities, which can be approximated as follows. Through table look-up, the smallest term, $lb$, is computed using the current input slew and zero driving capacitance; and the largest term, $ub$, using the current input slew and the maximum driving capacitance of $p$. Intermediate terms can be approximated based on a geometric sequence whose common ratio $r = (\frac{ub}{lb})^{\frac{1}{k}}$, where $k$ is a tunable parameter. In this contest, we have 8 terms in slew possibilities, and we set $k = 20$. The intermediate 6 terms are $lb\cdot r$, $lb\cdot r^3$, $lb\cdot r^5$, $lb\cdot r^8$, $lb\cdot r^{11}$, and $lb\cdot r^{15}$.

Recall that each output pin may have different slew targets for different timing corners and delay modes. The slew targets for different corners and delay modes can be set independently from each other.

By updating the slew targets properly, we can eliminate maximum slew violation by construction.

\begin{table*}
\caption{The Rising Slew Table for BUF\_X1 from Nangate 45nm Typical Corner}
\label{table:lib1}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
\diagbox{Input Transition}{Output Capacitance} & 0.365616 & 1.895430 & 3.790860 & 7.581710 & 15.163400 & 30.326900 & 60.653700 \\ \hline
1.23599 & 3.33809 & 5.59725 & 8.60523 & 14.8575 & 27.5164 & 52.8765 & 103.604 \\ \hline
4.43724 & 3.33727 & 5.59699 & 8.60578 & 14.8576 & 27.5188 & 52.8775 & 103.599 \\ \hline
15.6743 & 3.40246 & 5.62543 & 8.61689 & 14.8582 & 27.517 & 52.8787 & 103.599 \\ \hline
37.1331 & 4.36023 & 6.10464 & 8.84317 & 14.9465 & 27.5247 & 52.8726 & 103.605 \\ \hline
70.5649 & 5.85455 & 7.27833 & 9.43026 & 15.0988 & 27.6409 & 52.9322 & 103.603 \\ \hline
117.474 & 7.61897 & 9.14083 & 10.8314 & 15.5462 & 27.6912 & 53.0238 & 103.669 \\ \hline
179.199 & 9.58764 & 11.3565 & 13.0249 & 16.7347 & 27.8716 & 53.0513 & 103.775 \\ \hline
\end{tabular}
\vspace{-1em}
\end{table*}

\begin{table*}
\caption{The Rising Slew Table for BUF\_X2 from Nangate 45nm Typical Corner}
\label{table:lib2}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
\diagbox{Input Transition}{Output Capacitance} & 0.365616 & 3.786090 & 7.572190 & 15.144400 & 30.288800 & 60.577500 & 121.155000 \\ \hline
1.23599 & 3.10917 & 5.67693 & 8.71288 & 14.9785 & 27.635 & 52.969 & 103.657 \\ \hline
4.43724 & 3.10875 & 5.67786 & 8.71402 & 14.9788 & 27.6339 & 52.9719 & 103.66 \\ \hline
15.6743 & 3.20354 & 5.70984 & 8.72471 & 14.9811 & 27.631 & 52.9744 & 103.651 \\ \hline
37.1331 & 4.20264 & 6.15463 & 8.94062 & 15.0761 & 27.6468 & 52.967 & 103.666 \\ \hline
70.5649 & 5.70174 & 7.27713 & 9.47332 & 15.2076 & 27.7634 & 53.0379 & 103.659 \\ \hline
117.474 & 7.47026 & 9.1372 & 10.8172 & 15.6132 & 27.8134 & 53.1232 & 103.735 \\ \hline
179.199 & 9.44195 & 11.3787 & 12.9969 & 16.7387 & 27.9813 & 53.162 & 103.831 \\ \hline
\end{tabular}
\vspace{-1em}
\end{table*}

%Specifically, look at Figure~\ref{fig:slew}. When sizing the cell $c$, the downstream cells are already sized and the output capacitance is already available. However, the input slew $slew(q)$ also depends on the unknown predecessor size. As a result, the paper gives an estimation of slew at $p'$, under setup time constraint (and hold time constraint): $est\_slew_s(p')$ (and $est\_slew_h(p')$), based on the slew provided by timing analysis and its slew target, to decide the size of $c$:
%\begin{equation}
%est\_slew_s(p') = \theta slewt_s(p') - (1-\theta)slew(p'),
%\end{equation}
%and
%\begin{equation}
%est\_slew_h(p') = \theta slewt_h(p') - (1-\theta)slew(p'),
%\end{equation}
%where $\theta \in [0, 1]$ is a factor which can shift from pure slew target $\theta = 1$ to real timing analysis $\theta = 0$. Empirically, $\theta$ should be close to 1 initially since the cell sizes are actively changing, but close to 0 later when the cell sizes converge.

\subsection{Cell Assignment}

\subsubsection{Order of Sizing}
\label{sec:sizing_order}

Having the slew target updated, we now size the gates. Since output capacitance usually has larger impact on the cell timing than the input slew, we want to fix all the downstream gates of $g$ before sizing $g$. This requires a reverse topological order of all gates. However, if all the combinational logic and registers are included, then the circuit topology has cycles. We cut the cycles at the data inputs to registers in order to work with a directed acyclic graph (DAG), from which we define a reverse topological order for gates.

\subsubsection{Input Slew Estimation}
As the given cell libraries are of NLDM, and upstream gates of $g$ are not fixed yet, we need to estimate slews for each of $g$'s input pins. Figure~\ref{fig:slew} shows an example. Let $est\_slew(p) = \theta slewt(p) + (1-\theta)slew(p)$ be the estimated slew at output pin $p$, where $slew(p)$ is the slew of $p$ from STA, and $\theta \in [0,1]$ is a parameter that is close to 1 when gate sizing starts but close to 0 when gate sizing is about to converge. Then, $est\_slew(q) = est\_slew(p') + slew\_degrad(p', q)$, where $slew\_degrad(p', q)$ denotes the slew degradation due to the wire segment from $p'$ to $q$, which can be computed by the RC-tree model~\cite{TAU:Contest}.

\subsubsection{Cell Selection}

Let $out\_est\_slew(p)$ be the estimated output slew at pin $p$ through table look-up using the load seen by $p$ and $est\_slew(q)$, where $(q, p)$ is a timing arc. A pin may have different slew targets for each combination of timing corners and setup/hold time analysis, so use the corresponding one when sizing a gate at a specific corner.

\begin{itemize}
\item In setup time analysis, we select for gate $g$ the minimum size of equivalent cells such that $out\_est\_slew(p) \leq slewt(p)$ holds for all output pins $p$ of gate $g$ at the corner being considered. Then we choose the maximum sized cell from the selected cells across all corners for gate $g$ in setup time analysis. We define $size_{s}(g)$ as the cell size selected for $g$ in setup time analysis.

\item In hold time analysis, the selection works in the opposite way: we select the maximum size of equivalent cells such that $out\_est\_slew(p) \geq slewt(p)$ holds for all output pins $p$ of gate $g$ at the corner being considered; and then choose the minimum sized cell from the selected cells across all corners for gate $g$ in hold time analysis. We define $size_{h}(g)$ as the cell size selected for $g$ in hold time analysis.

\item If $size_{s}(g) \leq size_{h}(g)$, then assign the cell of size $size_{s}(g)$ to gate $g$. This is because any cell sizes in $[size_{s}(g), size_{h}(g)]$ satisfy both slew targets in setup time and hold time analysis. In order to minimize area and leakage power, we choose $size_{s}(g)$ for gate $g$.

\item If $size_{s}(g) > size_{h}(g)$, then assign the cell of size $size_{h}(g)$ to gate $g$. This is because there is no cell size that can satisfy both slew targets in setup time and hold time analysis at the same time. We honor hold time constraints in this case without sacrificing setup time seriously, since hold time violations cannot be fixed by adjusting the clock frequency.

\item The cell size for gate $g$ should not violate maximum capacitance limits for any of $g$'s output pins. Otherwise, the cell of minimum size without such violation is chosen for gate $g$.
\end{itemize}

%\begin{table*}
%\caption{The Delay Table for Buf\_X1 from Nangate 45nm Typical Corner}
%\label{table:lib}
%\centering
%\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
%\diagbox{Input Transition}{Output Capacitance} & 0.365616 & 1.895430 & 3.790860 & 7.581710 & 15.163400 & 30.326900 & 60.653700 \\ \hline
%1.23599 & 3.33809 & 5.59725 & 8.60523 & 14.8575 & 27.5164 & 52.8765 & 103.604 \\ \hline
%4.43724 & 3.33727 & 5.59699 & 8.60578 & 14.8576 & 27.5188 & 52.8775 & 103.599 \\ \hline
%15.6743 & 3.40246 & 5.62543 & 8.61689 & 14.8582 & 27.517 & 52.8787 & 103.599 \\ \hline
%37.1331 & 4.36023 & 6.10464 & 8.84317 & 14.9465 & 27.5247 & 52.8726 & 103.605 \\ \hline
%70.5649 & 5.85455 & 7.27833 & 9.43026 & 15.0988 & 27.6409 & 52.9322 & 103.603 \\ \hline
%117.474 & 7.61897 & 9.14083 & 10.8314 & 15.5462 & 27.6912 & 53.0238 & 103.669 \\ \hline
%179.199 & 9.58764 & 11.3565 & 13.0249 & 16.7347 & 27.8716 & 53.0513 & 103.775 \\ \hline
%\end{tabular}
%\vspace{-1em}
%\end{table*}

%\begin{table*}
%\caption{The Delay Table for Buf\_X2 from Nangate 45nm Typical Corner}
%\label{table:lib}
%\centering
%\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
%\diagbox{Input Transition}{Output Capacitance} & 0.365616 & 3.786090 & 7.572190 & 15.144400 & 30.288800 & 60.577500 & 121.155000 \\ \hline
%1.23599 & 3.10917 & 5.67693 & 8.71288 & 14.9785 & 27.635 & 52.969 & 103.657 \\ \hline
%4.43724 & 3.10875 & 5.67786 & 8.71402 & 14.9788 & 27.6339 & 52.9719 & 103.66 \\ \hline
%15.6743 & 3.20354 & 5.70984 & 8.72471 & 14.9811 & 27.631 & 52.9744 & 103.651 \\ \hline
%37.1331 & 4.20264 & 6.15463 & 8.94062 & 15.0761 & 27.6468 & 52.967 & 103.666 \\ \hline
%70.5649 & 5.70174 & 7.27713 & 9.47332 & 15.2076 & 27.7634 & 53.0379 & 103.659 \\ \hline
%117.474 & 7.47026 & 9.1372 & 10.8172 & 15.6132 & 27.8134 & 53.1232 & 103.735 \\ \hline
%179.199 & 9.44195 & 11.3787 & 12.9969 & 16.7387 & 27.9813 & 53.162 & 103.831 \\ \hline
%\end{tabular}
%\vspace{-1em}
%\end{table*}

\subsection{Convergence}
\label{sec:sizing_converge}
After cell selection for all gates, we run STA again. If the worst negative slack improves for all corners, we proceed to next round of gate sizing using the current cell assignment. Otherwise, we score the current cell assignment by a linear combination of worst negative slack, average total negative slack over all path endpoints, and average cell area over all gates. The lower the score, the better. If the score decreases for all corners, we also proceed to next round of gate sizing using the current cell assignment. If not, we revert to the previous cell assignment and quit gate sizing.

%Again, since our problem considers multiple corners, after we get the sizing solution for each corner, we must take the maximum sizing for each cell across different corners to make sure that the sizing solution satisfies the slew targets for all the corners.

%Since the paper focuses on fixing setup time violations. We generalize the method by using similar method such that it also address the hold time violation. Instead, $slewt(p)$ are initialized to 0 and the cell assignment is also opposite to that in setup violation removal step: we choose the maximum cell size that gives the output slew $slew(p)$ such that $slew(p) \geq slewt(p)$, and take the minimum sizing for each cell across different corners to satisfy the slew target for hold time constraint for all the corners.
%
%The gate sizing solution under setup time constraint gives the upper bound for sizing of each cell, and that under hold time constraint gives the lower bound for sizing of each cell. I
%Initially, when the sizing of predecessors are actively changing, both $slewt(p')$ and $slew(p')$ contribute much to the actual slew at $p'$. Later when the sizing of predecessors become stable,


%The slew targets $slewt(p')$ and $slewt(p)$ are assigned for both $p'$ and $p$ and we can then use the formula presented in~\cite{TAU:Contest} to calculate $q$. To assign a size to the cell $c$, notice that at this time, the downstream cells have all been assigned and the output capacitance seen at $p$ is fixed and known. We can then use the table look-up in the cell library to determine the smallest cell size that gives the output slew $slew(p)$ such that $slew(p) \leq slewt(p)$. After gate(cell) sizing assignment, the timing analysis based on the design with new gate(cell) sizes, and refine the slew target for the next round of gate sizing assignment. This iterative process terminates until some stopping criterion is met.
\begin{figure}
\center
\begin{tikzpicture}[align=center, font=\footnotesize, node distance = 2cm]
  \node [module] (1) {}    ;
  \node [module] (2) [below right=-0.9cm and 1.5cm of 1] {$c$}  ;
  \draw [very thick] (1.east) -- ++(1, 0) node[pos=0.0, above right]{$p'$} -- ++(0, 0.4) -- ++(0.5, 0);
  \draw [very thick] (1.east) -- ++(1, 0) -- ++(0, -0.4) -- ++(0.5, 0) node[pos=0.1, below right]{$q$};
  \draw [very thick] ([yshift=-0.4cm]2.west) -- ++(-0.5, 0);
  \draw [very thick] ([yshift=-0.4cm]1.west) -- ++(-0.5, 0);
  \draw [very thick] ([yshift=0.4cm]1.west) -- ++(-0.5, 0);
  \draw [very thick] (2.east) -- ++(0.5, 0) node[pos=0.0, above right]{$p$};
\end{tikzpicture}
\caption{A Cell $c$ and a Predecessor}
\label{fig:slew}
\end{figure}

%Given a net of $N$ nodes with capacitance $C_1, C_2, ... C_N$, and the output slew $s_o$ of node $o \in O$, the input slew $s_i$ of the wire can be estimated using the formula presented in~\cite{TAU:Contest}.
%\begin{equation}
%\label{itoo}
%s_i = \sqrt{s_o^2 + d_o^2 - 2\beta_o}
%\end{equation}
%where $d_o$ is the Elmore Delay from the input to the output:
%\begin{equation}
%d_o = \Sigma_{k \in N}R_{shared}C_k,
%\end{equation}
%and $\beta$ can be calculated using the same equation, but replacing all $C_k's$ term by $C_kd_k$:
%\begin{equation}
%\beta_o = \Sigma_{k \in N}R_{shared}C_kd_k.
%\end{equation}
%For multi-output nets, the $s_i$ value should be taken as the minimum across the values calculated by given different output $o$ because all the output slew target have to be satisfied. In other words,
%\begin{equation}
%\label{itoo}
%s_i = \min_{o \in P}\{\sqrt{s_o^2 + d_o^2 - 2\beta_o}\}
%\end{equation}

%The algorithm terminates when the stopping criterion is met: 1. the worst slack becomes worse and 2. the absolute sum of negative slacks divided by the number of end points and the average cell area increases. Then, the assignment of the previous iteration, which achieves the best present objective value, is recovered. Such a method avoids incremental timing updates, and is thus more timing efficient.



